Abstract Data Type Inference

### 2015-02-27 draft.tex
Added the major theorems.
Optimized packages.
New section for computing matching functions.
Section titles.
Abstract plus a couple citations.

\documentclass[10pt,preprint,nocopyrightspace]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{balance}
\usepackage{hyperref}
\usepackage{url}
\usepackage{breakurl}
\usepackage{amsmath}

@@

  TODO WRITE THE ABSTRACT

@@

\input intro
\input inference
\input embedding
\input computing
\input empirical
\input related

@@

>>>>

\documentclass[10pt,preprint,nocopyrightspace,natbib,authoryear]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

  Checking that efficient implementations of concurrent objects adhere to their
  abstract data types (ADTs) can be made tractable when ADTs are given by
  symbolic, logical representations. Such representations are however difficult
  to obtain. Common practice is to design reference implementations.

  In this work we demonstrate that effective symbolic ADT representations can
  be automatically extracted from the executions of reference implementations.
  Our approach exploits key features of naturally-occurring ADTs: violations
  can be decomposed into a small set of representative patterns, and these
  patterns manifest in executions with few operations. By identifying certain
  algebraic properties of naturally-occurring ADTs, and exhaustively sampling
  executions up to a small number of operations, we extract concise symbolic
  ADT representations which are complete in practice.

@@

\input intro
\input inference
\input algebra
\input algorithm
\input matching
\input empirical
\input related

@@

% \balancecolumns

### 2015-02-27 intro.tex
Abstract plus a couple citations.

Recent work has demonstrated that checking observational refinement can be
performed efficiently in practice, given symbolic ADT representations,
e.g.,~using first-order logic. However, writing accurate symbolic
specifications is an expected challenge for the designers of concurrent ADTs.
Common practice is to write reference implementations. Mapping these imperative
implementations to the logical formulæ describing valid executions is a great
challenge for human developers.

>>>>

Recent work has demonstrated that checking observational refinement can be
performed efficiently in practice, given symbolic ADT representations,
e.g.,~using first-order logic~\cite{conf/popl/BouajjaniEEH15,
conf/pldi/EmmiEH15}. However, writing accurate symbolic specifications is an
expected challenge for the designers of concurrent ADTs. Common practice is to
write reference implementations. Mapping these imperative implementations to
the logical formulæ describing valid executions is a great challenge for human
developers.
